### 2016-09-07 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
final small edits before submitting
incorporated bibliography
Copy-and-paste of generated bbl file into tex source as required by PLOS

\bibliography{references}

>>>>

\begin{thebibliography}{10}

\bibitem{coltonwiggins12}
Colton S, Wiggins GA.
\newblock Computational Creativity: The Final Frontier?
\newblock In: Proceedings of 20th European Conference on Artificial
  Intelligence (ECAI). Montpellier, France; 2012. p. 21--26.

\bibitem{colton08}
Colton S.
\newblock Creativity versus the Perception of Creativity in Computational
  Systems.
\newblock In: Proceedings of AAAI Symposium on Creative Systems; 2008. p.
  14--20.

\bibitem{widmerAIM09}
Widmer G, Flossmann S, Grachten M.
\newblock {YQX} Plays {Chopin}.
\newblock AI Magazine. {2009};{30}({3}):35--48.

\bibitem{leon10MM}
Le\'on C, Gerv\'as P.
\newblock The Role of Evaluation-Driven Rejection in the Successful Exploration
  of a Conceptual Space of Stories.
\newblock Minds and Machines. 2010;20(4):615--634.

\bibitem{perezyperez99}
P\'erez~y P\'erez R.
\newblock MEXICA: A Computer Model of Creativity in Writing [PhD thesis].
\newblock University of Sussex. Brighton, UK; 1999.

\bibitem{cardoso09}
Cardoso A, Veale T, Wiggins GA.
\newblock Converging on the Divergent: The History (and Future) of the
  International Joint Workshops in Computational Creativity.
\newblock AI Magazine. 2009;30(3):15--22.

\bibitem{rhodes61}
Rhodes M.
\newblock An analysis of creativity.
\newblock Phi Delta Kappan. 1961;42(7):305--310.

\bibitem{torrance67}
Torrance EP.
\newblock Scientific Views of Creativity and Factors Affecting its Growth.
\newblock In: Kagan J, editor. Creativity and Learning. Boston: Beacon Press;
  1967. p. 73--91.

\bibitem{plucker04defn}
Plucker JA, Beghetto RA, Dow GT.
\newblock Why Isn't Creativity More Important to Educational Psychologists?
  {Potentials}, Pitfalls, and Future Directions in Creativity Research.
\newblock Educational Psychologist. 2004;39(2):83--96.

\bibitem{kaufman09}
Kaufman JC.
\newblock Creativity 101.
\newblock The Psych 101 series. New York: Springer; 2009.

\bibitem{hennessey10}
Hennessey BA, Amabile TM.
\newblock Creativity.
\newblock Annual Review of Psychology. 2010;61:569--598.

\bibitem{plucker04}
Plucker JA, Beghetto RA.
\newblock Why Creativity is Domain General, Why it Looks Domain Specific, and
  why the Distinction Doesn't Matter.
\newblock In: Sternberg RJ, Grigorenko EL, Singer JL, editors. Creativity: From
  Potential to Realization. Washington, DC: American Psychological Association;
  2004. p. 153--167.

\bibitem{lakoff87}
Lakoff G.
\newblock Women, Fire and Dangerous things: What Categories reveal about the
  mind.
\newblock Chicago, IL: University of Chicago Press; 1987.

\bibitem{wittgenstein58}
Wittgenstein L.
\newblock {Philosophical Investigations, eds. Anscombe, G. E. M. and Rhees, R.
  and {Von Wright}, G. H.}
\newblock 2nd ed. Oxford, UK: Basil Blackwell; 1958.

\bibitem{torrance88}
Torrance EP.
\newblock The Nature of Creativity as Manifest in its testing.
\newblock In: Sternberg RJ, editor. The Nature of Creativity. Cambridge, UK:
  Cambridge University Press; 1988. p. 43--75.

\bibitem{sternberg99a}
Sternberg RJ, Lubart TI.
\newblock The Concept of Creativity: Prospects and Paradigms.
\newblock In: Sternberg RJ, editor. Handbook of Creativity. Cambridge, UK:
  Cambridge University Press; 1999. p. 3--15.

\bibitem{vartanian14}
Vartanian O.
\newblock Toward a Cumulative Psychological Science of Aesthetics, Creativity,
  and the Arts.
\newblock Psychology of Aesthetics, Creativity, and the Arts. 2014;8(1):15--17.

\bibitem{stein63}
Stein MI.
\newblock A Transactional Approach to Creativity.
\newblock In: Taylor CW, Barron F, editors. Scientific Creativity: Its
  Recognition and Development. New York: John Wiley \& Sons; 1963. p. 217--227.

\bibitem{boden04}
Boden MA.
\newblock The creative mind: Myths and mechanisms.
\newblock 2nd ed. London, UK: Routledge; 2004.

\bibitem{guilford50}
Guilford JP.
\newblock Creativity.
\newblock American Psychologist. 1950;5:444--454.

\bibitem{torrance74}
Torrance EP.
\newblock Torrance Tests of Creative Thinking.
\newblock Bensenville, IL: Scholastic Testing Service; 1974.

\bibitem{pease01}
Pease A, Winterstein D, Colton S.
\newblock Evaluating Machine Creativity.
\newblock In: Proceedings of Workshop Program of ICCBR-Creative Systems:
  Approaches to Creativity in AI and Cognitive Science; 2001. p. 129--137.

\bibitem{wiggins06ngc}
Wiggins GA.
\newblock Searching for computational creativity.
\newblock New Generation Computing. 2006;24(3):209--222.

\bibitem{peinado06ngc}
Peinado F, Gervas P.
\newblock {Evaluation of automatic generation of basic stories}.
\newblock New Generation Computing. {2006};{24}({3}):{289--302}.

\bibitem{ritchie07}
Ritchie G.
\newblock Some Empirical Criteria for Attributing Creativity to a Computer
  Program.
\newblock Minds and Machines. 2007;17:67--99.

\bibitem{mayer99}
Mayer RE.
\newblock Fifty Years of Creativity Research.
\newblock In: Sternberg RJ, editor. Handbook of Creativity. Cambridge, UK:
  Cambridge University Press; 1999. p. 449--460.

\bibitem{dietrich10}
Dietrich A, Kanso R.
\newblock A review of {EEG}, {ERP}, and Neuroimaging Studies of Creativity and
  Insight.
\newblock Psychological Bulletin. 2010;136(5):822--848.

\bibitem{gabora12}
Gabora L, O'Connor B, Ranjan A.
\newblock The recognizability of individual creative styles within and across
  domains.
\newblock Psychology of Aesthetics, Creativity, and the Arts.
  2012;6(4):351--360.

\bibitem{mccormack07}
McCormack J.
\newblock Creative Ecosystems.
\newblock In: Proceedings of the 4th International Joint Workshop on
  Computational Creativity. London, UK; 2007. p. 129--136.

\bibitem{sosa09}
Sosa R, Gero J, Jennings K.
\newblock Growing and Destroying the Worth of Ideas.
\newblock In: Proceedings of the 7th ACM Creativity and Cognition conference.
  Berkeley, California; 2009. p. 295--304.

\bibitem{plucker98}
Plucker JA.
\newblock Beware of Simple Conclusions: The Case for Content Generality of
  Creativity.
\newblock Creativity Research Journal. 1998;11(2):179--182.

\bibitem{baer98}
Baer J.
\newblock The Case for Domain Specificity of Creativity.
\newblock Creativity Research Journal. 1998;11(2):173--177.

\bibitem{baer10}
Baer J.
\newblock Is Creativity Domain-Specific?
\newblock In: Kaufman JC, Sternberg RJ, editors. The Cambridge Handbook of
  Creativity. New York, NY: Cambridge University Press; 2010. p. 321--341.

\bibitem{poincare29}
Poincar\'e H.
\newblock Mathematical Creation.
\newblock In: The Foundations of Science: Science and Hypothesis, The Value of
  Science, Science and Method.. vol. Science and Method [Original French
  version published 1908, Authorized translation by George Bruce Halsted]. New
  York: The Science Press; 1929. p. 383--394.

\bibitem{hadamard45}
Hadamard J.
\newblock An Essay on the Psychology of Invention in the Mathematical Field.
\newblock Princeton, NJ: Princeton University Press; 1945.

\bibitem{weisberg88}
Weisberg RW.
\newblock Problem Solving and Creativity.
\newblock In: Sternberg RJ, editor. The Nature of Creativity. Cambridge, UK:
  Cambridge University Press; 1988. p. 148--176.

\bibitem{bryankinns09}
Bryan-Kinns N.
\newblock {Everyday Creativity}.
\newblock In: Bryan-Kinns N, Gross MD, Johnson H, Ox J, Wakkary R, editors.
  Proceedings of the 7th ACM conference on Creativity and Cognition. Berkeley,
  California: ACM; 2009. p. iii--iv.

\bibitem{mooney63}
Mooney RL.
\newblock A Conceptual Model for Integrating Four Approaches to the
  Identification of Creative Talent.
\newblock In: Taylor CW, Barron F, editors. Scientific Creativity: Its
  Recognition and Development. New York: John Wiley \& Sons; 1963. p. 331--340.

\bibitem{odena09}
Odena O, Welch G.
\newblock A Generative Model of Teachers' Thinking on Musical Creativity.
\newblock Psychology of Music. 2009;37(4):416--442.

\bibitem{jordanous16cs}
Jordanous A.
\newblock Four PPPPerspectives on Computational Creativity in theory and in
  practice.
\newblock Connection Science. 2016;tbc(tbc).

\bibitem{wallas26}
Wallas G.
\newblock The Art of Thought.
\newblock 1st ed. London, UK: Jonathan Cape; 1926.

\bibitem{goldman64}
Goldman RJ.
\newblock The {M}innesota Tests of Creative Thinking.
\newblock Educational Research. 1964;7(1):3--14.

\bibitem{guilford67}
Guilford JP.
\newblock The nature of human intelligence.
\newblock New York, NY: McGraw-Hill; 1967.

\bibitem{amabile96}
Amabile TM.
\newblock Creativity in context.
\newblock Boulder, Colorado: Westview Press; 1996.

\bibitem{gallie56}
Gallie WB.
\newblock Essentially Contested Concepts.
\newblock Proceedings of the Aristotelian Society. 1956;56:167--198.
\newblock Available from: \url{http://www.jstor.org/stable/4544562}.

\bibitem{firth57}
Firth JR.
\newblock A synopsis of linguistic theory, 1930-1955.
\newblock Studies in Linguistic Analysis. 1957;p. 1--32.

\bibitem{lakoff80}
Lakoff G, Johnson M.
\newblock Metaphors we live by.
\newblock Chicago, IL: University of Chicago Press; 1980.

\bibitem{oakes98}
Oakes MP.
\newblock Statistics for Corpus Linguistics.
\newblock Edinburgh, UK: Edinburgh University Press; 1998.

\bibitem{rayson00}
Rayson P, Garside R.
\newblock Comparing Corpora using Frequency Profiling.
\newblock In: Kilgarriff A, Sardinha TB, editors. Proceedings of ACL Workshop
  on Comparing Corpora. vol.~9. ACL. Hong Kong: ACM; 2000. p. 1--6.

\bibitem{kilgarriff01}
Kilgarriff A.
\newblock Comparing Corpora.
\newblock International Journal of Corpus Linguistics. 2001;6(1):97--133.

\bibitem{kilgarriff06}
Kilgarriff A.
\newblock Where to go if you would like to find out more about a word than the
  dictionary tells you.
\newblock Macmillan English Dictionary Magazine. 2006;Issue 35 (Jan-Feb).

\bibitem{ivcevic09}
Ivcevic Z.
\newblock Creativity Map: Toward the Next Generation of Theories of Creativity.
\newblock Psychology of Aesthetics, Creativity, and the Arts. 2009;3(1):17--21.

\bibitem{garfield72}
Garfield E.
\newblock Citation analysis as a tool in journal evaluation.
\newblock Science. 1972;178(60):471--479.

\bibitem{hirsch05}
Hirsch JE.
\newblock An index to quantify an individual's scientific research output.
\newblock Proceedings of the National Academy of Sciences of the United States
  of America. 2005;102(46):16569--16572.

\bibitem{briscoe06}
Briscoe T, Carroll J, Watson R.
\newblock The Second Release of the {RASP} System.
\newblock In: Curran J, editor. Proceedings of the COLING/ACL 2006 Interactive
  Presentation Sessions. ACL. Sydney, Australia: ACM; 2006. p. 77--80.

\bibitem{dunning93}
Dunning T.
\newblock Accurate Methods for the Statistics of Surprise and Coincidence.
\newblock Computational Linguistics. 1993;19(1):61--74.

\bibitem{jordanous10a}
Jordanous A.
\newblock Defining Creativity: Finding Keywords for Creativity Using Corpus
  Linguistics Techniques.
\newblock In: Proceedings of the International Conference on Computational
  Creativity. Lisbon, Portugal; 2010. p. 278--287.

\bibitem{lin98}
Lin D.
\newblock An information-theoretic definition of similarity.
\newblock In: Proceedings of the 15th International Conference on Machine
  Learning. Madison, WI; 1998. p. 296--304.

\bibitem{harris68}
Harris Z.
\newblock Mathematical Structures of Language.
\newblock New York: Wiley; 1968.

\bibitem{kilgarriff00}
Kilgarriff A, Yallop C.
\newblock What's in a thesaurus.
\newblock In: Proceedings of the Second Conference on Language Resources and
  Evaluation (LREC-00). Athens; 2000. p. 1371--1379.

\bibitem{leech92}
Leech G.
\newblock 100 million words of {English}: the {British National Corpus (BNC)}.
\newblock Language Research. 1992;28(1):1--13.

\bibitem{weeds03}
Weeds JE.
\newblock Measures and Applications of Lexical Distributional Similarity [PhD
  thesis].
\newblock Informatics, University of Sussex. Brighton, UK; 2003.

\bibitem{mannschu99}
Manning C, Sch{\"u}tze H.
\newblock Foundations of Statistical Natural Language Processing.
\newblock Cambridge, MA: MIT Press; 1999.

\bibitem{weedsweir03}
Weeds J, Weir D.
\newblock Finding and evaluating nearest neighbours.
\newblock In: Archer D, Rayson P, Wilson A, McEnery T, editors. Proceedings of
  the 2nd International Conference of Corpus Linguistics. Lancaster, UK: UCREL;
  2003. p. 879--888.

\bibitem{mccanavi09}
McCarthy D, Navigli R.
\newblock The {English} lexical substitution task.
\newblock Language Resources and Evaluation: Special Issue on Computational
  Semantic Analysis of Language. 2009;43(3):139--159.

\bibitem{biemann06}
Biemann C.
\newblock Chinese {Whispers}: an efficient graph clustering algorithm and its
  application to natural language processing problems.
\newblock In: Proceedings of TextGraphs: the First Workshop on Graph Based
  Methods for Natural Language Processing. Morristown, NJ: Association for
  Computational Linguistics; 2006. p. 73--80.

\bibitem{mackinnon70}
MacKinnon DW.
\newblock Creativity: a Multi-Faceted Phenomenon.
\newblock In: Roslansky JD, editor. Creativity: A Discussion at the Nobel
  Conference. Amsterdam, The Netherlands: North-Holland Publishing Company;
  1970. p. 17--32.

\bibitem{jordanous12jims}
Jordanous A, Keller B.
\newblock What makes musical improvisation creative?
\newblock Journal of Interdisciplinary Music Studies. 2012;6:151--175.

\bibitem{fellbaum98}
Fellbaum C, editor.
\newblock WordNet: An electronic lexical database.
\newblock Cambridge, MA: The MIT press; 1998.

\bibitem{miller08}
Miller P, Styles R, Heath T.
\newblock Open data commons, a license for open data.
\newblock In: Bizer C, Heath T, Idehen K, Berners-Lee T, editors. Proceedings
  of the WWW2008 Workshop on Linked Data on the Web. vol. 369 of CEUR-WS.
  Beijing, China: CEUR; 2008. p.~8.

\bibitem{jordanous12cc}
Jordanous A.
\newblock A Standardised Procedure for Evaluating Creative Systems:
  Computational Creativity Evaluation Based on What it is to be Creative.
\newblock Cognitive Computation. 2012;4(3):246--279.

\bibitem{jordanousphd}
Jordanous A.
\newblock Evaluating Computational Creativity: A Standardised Procedure for
  Evaluating Creative Systems and its Application [PhD thesis].
\newblock University of Sussex. Brighton, UK; 2012.

\bibitem{jordanous16aisb}
Jordanous A.
\newblock The longer term value of creativity judgements in computational
  creativity.
\newblock In: al~Rifaie MM, McGregor S, editors. {AISB} Symposium on
  Computational Creativity (CC2016). Sheffield, UK: AISB; 2016. p. 16--23.

\bibitem{boden99}
Boden MA.
\newblock Introduction [summary of {B}oden's keynote address to {AISB}'99].
\newblock In: AISB Quarterly - Special issue on AISB99: Creativity in the arts
  and sciences. vol. 102; 1999. p.~11.

\bibitem{jordanous15vem}
Jordanous A, Allington D, Dueck B.
\newblock Measuring cultural value using social network analysis: a case study
  on valuing electronic musicians.
\newblock In: Proceedings of the Sixth International Conference on
  Computational Creativity June; 2015. p. 110.

\bibitem{panglee08}
Pang B, Lee L.
\newblock Opinion mining and sentiment analysis.
\newblock Foundation and Trends in Information Retrieval. 2008;2(1-2):1--135.

\end{thebibliography}

%\bibliography{references}
